Creating More Meaningful Explanations for Audio Deepfake Detection

### 2025-01-20 draft.tex
small changes

			The black-box model described in the previous section was trained on the first 10,000
			samples out of the aforementioned dataset, with evaluation being performed on the
			remaining 21,778. Training batches consisted of 100 samples each with every window
			position for each sample and an upper limit of 1,000,000 lines per batch. For each
			batch, two epochs were performed. Because a single sample can have multiple input
			lines, evaluation cannot be performed on a per-line basis, but must instead be
			summarized. Two methods are possible: median and mean, with the difference in results
			being negligible in my experiments. The default threshold is 0.5, meaning that a
			result under 0.5 is a false result and over 0.5 is a true result. This threshold can
			however be adjusted, useful for computing the EER.

>>>>

			The black-box model described in the previous section was trained on the first 3474
			samples in the dataset, with the stopping point being determined by finding the global
			minimum of the validation accuracy during training. Evaluation was then performed on
			the remaining samples in the dataset. Training batches consisted of 100 samples each
			with every window position for each sample and an upper limit of 1,000,000 lines per
			batch. For each batch, two epochs were performed. Because a single sample can have
			multiple input lines, evaluation cannot be performed on a per-line basis, but must
			instead be summarized. Two methods are possible: median and mean, with the difference
			in results being negligible in my experiments. The default threshold is 0.5, meaning
			that a result under 0.5 is a false result and over 0.5 is a true result. This
			threshold can however be adjusted, useful for computing the EER.
